\mytitle

### 2012-03-23 papers/SAS2012/implicitization.tex
nouveaux chiffres, et commentaires mis à jour

Let us briefly comment the results given in more details in Table~\ref{tab:techniques} and Figure~\ref{fig:techniques}.
\emph{Guided Static Analysis} from \cite{DBLP:conf/sas/GopanR07} improves the
result of the classical Abstract Interpretation in $2.72\%$ of the control points
in $P_R$.
\emph{Path-focusing} from \cite{Monniaux_Gonnord_SAS11} gives
statistically better results, and finds better invariants than \emph{Guided
Static Analysis} in $9.89\%$ of the cases. However, it also loses precision in an
important number ($2.68\%$) of control points.
Finally, our combined technique gives the most promising results, since it is
statistically more precise than the other techniques.

The analysis using disjunctive invariants greatly improves the
precision of the analysis (for $12.06\%$ of the control points in $P_R$), at an
acceptable time cost (see Table \ref{tab:time}). \MM{TODO}

While experiencing with techniques that use SMT-solving, we encountered some
limitations due to non-linear arithmetic in the analyzed programs. Indeed, 
the SMT-solver is not able to decide the satisfiability of some SMT-formulae
expressing the semantics of non-linear programs. 
In this case, we skipped the functions for which the SMT-solver returned the
``unknown'' result.
This limitation occurred very rarely in our experiments, except for the analysis
of \emph{Lapack/Blas}, where 798 over the 1602 functions have been skipped.
\emph{Lapack/Blas} implements matrix computations, which use floating-point multiplications.

@@

Table \ref{tab:time} \MM{TODO} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} are sometimes faster than the classical
algorithm.
This seems due to the fact that these algorithms start on a small subset
of the graph, and then may need fewer iterations on the complete graph.
The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.

>>>>

Let us briefly comment the results given in more details in Table~\ref{tab:techniques} and Figure~\ref{fig:techniques}.
\emph{Guided Static Analysis} from \cite{DBLP:conf/sas/GopanR07} improves the
result of the classical Abstract Interpretation in $2.21\%$ of the control points in $P_R$.
\emph{Path-focusing} from \cite{Monniaux_Gonnord_SAS11} gives
statistically better results, and finds better invariants than \emph{Guided
Static Analysis} in $5.00\%$ of the cases. However, it also loses
precision compared to \emph{Guided Static Analysis}  in an
important number ($4.00\%$) of control points.

Unfortunately, these two techniques are less precise than the classical analysis
in a important number of cases ($4.64\%$ for $G$, $5.14\%$ for $PF$).
This could be explained by the non-monotonicity of the results with widening operators.

Finally, our combined technique gives the most promising results, since it is
statistically more precise than the other techniques.

The analysis using disjunctive invariants greatly improves the
precision of the analysis (for $14.46\%$ of the control points in $P_R$), at an
acceptable time cost compared to our combined algorithm (see Table \ref{tab:time}). \MM{TODO}

While experiencing with techniques that use SMT-solving, we encountered some
limitations due to non-linear arithmetic in the analyzed programs. Indeed, 
the SMT-solver is not able to decide the satisfiability of some SMT-formulae
expressing the semantics of non-linear programs. 
In this case, we skipped the functions for which the SMT-solver returned the
``unknown'' result.
This limitation occurred very rarely in our experiments, except for the analysis
of \emph{Lapack/Blas}, where 668 over the 1498 functions have been skipped.
\emph{Lapack/Blas} implements matrix computations, which use floating-point multiplications.

@@

Table \ref{tab:time} \MM{TODO} gives the execution time of the different analysis
techniques. It is interesting to see that 
\emph{Path-focusing} technique is sometimes faster than the classical algorithm.
This seems due to the fact that this technique avoids many convex hulls, which
is costly, and also computes the image of an abstract value by an entire path
instead of many single transitions.
The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.
